Scientific Reasoning with LLMs

### 2024-10-29 docs/proposal/main.tex
RS1&2

\section{Methodology}
We postulate the following research questions: 
RQ1: Can smaller student LLMs be still effective at few-shot prompting for scientific reasoning?
RQ2: How does their performance compare with that of a teacher model?
RQ3: Can an LLM-agent's behavior be distilled into a single model?
\paragraph{RQ1} 
We plan to

>>>>

\section{Methodology}
We postulate the following research questions: 
RQ1: Can we build a LLM Agent to improve the LLMs performance on science questions?
RQ2: Does Soft Prompting improve the performance of the LLM (Agent)?
RQ3: Can an LLM-agent's behavior be distilled into a single model?
\paragraph{RQ1} 
We plan to
